\documentclass[letterpaper]{moderncv}

\usepackage{textcomp}

\moderncvstyle{classic}
\moderncvcolor{black}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.80]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvheadnamewidth}{10cm}            % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Arshdeep}{Singh}
\address{}{Toronto, ON}{}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\phone[mobile]{+1~(647)~293~8485}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
\email{arshwaraich12@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{arshwaraich.com}                         % optional, remove / comment the line if not wanted
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Hiring Manager}{Unilever\\Corp Headquarters\\Toronto, ON}
\date{\today}
\opening{Dear Hiring Manager:}
\closing{Sincerely,}
\enclosure[Attached]{CV}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

I would like to express my immense interest towards the Software Engineer internship position in Collective Intelligence at Unilever Inc. for the fall 2020 term. Being currently enrolled in a bachelor’s of technology degree in Software Development at Seneca College, having had experience working in the software development industry and having previously worked as a Research Assistant under Seneca Applied Research, I am confident I will be an asset to your various initiatives.

I enjoy investigating complex problems and collaborating with cross functional teams to arrive at practical, creative and innovative solutions. I frequently leverage my software engineering and programming skills to develop, code and test exceptional cloud-based systems.

I believe my skill-set closely reflects your listed requirements for this position, some of which I would like to list are:

{\begin{itemize}%
	\item I am a 4 th year student in Seneca College’s excellent Software Development degree program, a program built around strong software development and programming skills.
	\item I have had experience working as a front-end Angular developer for a multi-role insurance portal with Mixto Card Conceptions Inc., a 20 year old business solutions company based in Mississauga, ON.
	\item Worked as a team lead to design, develop, document and deploy a full-stack system with a team of three for NexusHealth Inc. Consisting of a robust front-end web and mobile application based solution using ReactJS and React Native, a RESTful web API, a NoSQL database as well as a serverless back-end architecture. Employing Object Oriented programming principles, appropriate data structures and algorithms as well as Git based version control systems.
	\item The ability to effectively collaborate well with others, leveraging exceptional interpersonal, organizational and analytical skills.
	\end{itemize}}
	
I’ve attached a copy of my resume that details my projects and experience in software development. I can be reached anytime via email at arshwaraich12@gmail.com or via phone, at +1(647)-293-8485. Thank you for your time and consideration. I look forward to speaking with you about this opportunity.

\makeletterclosing
\end{document}

