\documentclass[letterpaper]{moderncv}

\usepackage{textcomp}

\moderncvstyle{classic}
\moderncvcolor{black}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.80]{geometry}

\name{Arshdeep Singh}{}
% \address{Toronto, ON}
\phone[mobile]{(647) 293-8485}
\email{work@arshwaraich.com}
\homepage{arshwaraich.com}
    \begin{document}
\makecvtitle

\section{Summary}
\cvitem{}{Software Developer II with 5+ years building full-stack solutions in fintech and payments. Delivered high-impact projects spanning authentication and security at Stripe (Email OTP and User Security Framework: 26M+ users), the HSBC acquisition at RBC (\$1B+ AUM), and Canada's first FHSA platform. Experienced in React, Ruby, .NET, AWS, and large-scale auth systems, with a focus on scalable, accessible solutions.}

\section{Work Experience}
\cventry
{May 2025 -- Present}
{Software Developer II}
{Stripe}
{Toronto, ON}
{}
{Frequently tapped to lead time-sensitive UAX projects end-to-end, recognised for ramping fast into unfamiliar auth surfaces and shipping under tight deadlines.
\begin{itemize}%
	\item Shipped Email OTP as a new authentication factor on Stripe Connect (DRI), replacing SMS as the only available option; replaced \$96K/month in international SMS costs and materially reduced SMS-based fraud.
	\item Led integration of Stripe's User Security Framework (USF) into Connect, delivering a security upgrade to 26M+ users on schedule; designed a generalized signal-ingestion approach and observability dashboards adopted by partner teams.
	\item Designed and shipped a new email-based bank account verification flow on a one-month, two-sprint deadline, automating a previously manual support process for users without enough info on file to verify themselves; rolled out safely from 1\% to 100\% globally and cut support volume.
	\item Contributed to a Human-in-the-Loop system that requires user confirmation on sensitive agent-initiated API calls; built UI components and ran LLM evals to validate that agent prompts reliably produced the correct downstream tool calls.
	\item Currently leading work to harden Stripe's API key model for agentic use: introducing per-key access policies and elevating granular restricted keys to first-class by deprecating the legacy all-permissions secret key.
	\end{itemize}}
\cventry
{Aug 2023 -- May 2025}
{Senior Software Developer}
{Royal Bank of Canada}
{Toronto, ON}
{}
{\begin{itemize}%
	\item Contributed to the largest acquisition in Canadian banking history, integrating HSBC clients into the RBC Direct Investing platforms, adding \$1B+ to AUM while ensuring on-time delivery with reusable development, agile feature toggles, and modern React patterns.
	\item Redesigned the Direct Investing homepage using a scalable design framework, incorporating responsive and accessible elements to improve user engagement.
	\item Assisted in enabling foreign market trading, expanding global reach.
	\end{itemize}}
\cventry
{Sep 2021 -- Aug 2023}
{Software Developer}
{Royal Bank of Canada}
{Toronto, ON}
{}
{\begin{itemize}%
	\item Led front-end changes for Canada's first-to-market First Home Savings Account (FHSA) on RBC InvestEase, delivering within 4 months and enabling \$100M in Q1 investments.
	\item Developed bulk account approvals, reducing manual processing by 40\%.
	\end{itemize}}
\cventry
{Jan 2021 -- Apr 2021}
{Software Developer Co-Op}
{Royal Bank of Canada}
{Toronto, ON}
{}
{\begin{itemize}%
	\item Engineered Java Spring batch data migration tools for legacy system decommissioning, significantly reducing QA workload.
	\item Selected to meet RBC's Group Head of Technology \& Operations for exceptional performance.
	\end{itemize}}
\cventry
{May 2020 -- Aug 2020}
{Software Developer Co-Op}
{Portable Intelligence Inc.}
{Markham, ON}
{}
{\begin{itemize}%
	\item Developed proof-of-concept UDP protocol integration layer for Artemis computer vision system, creating new revenue stream for company.
	\item Implemented automated software update system, eliminating need for on-site client visits and saving hundreds of man-hours annually.
	\end{itemize}}

\section{Education}
\cventry
{Jan 2018 -- Aug 2021}
{Honours Bachelor of Technology – Software Development (BSD)}{Seneca College}{Toronto, ON}{}
{\begin{itemize}%
	\item GPA: 4.0
	\item President's Honour List: Fall 2018 - Summer 2021
	\end{itemize}}

\section{Skills}
\cvitem{Languages}{Ruby · C\# · JavaScript/TypeScript · HTML/CSS · Java · C/C++ · Python}
\cvitem{Frameworks}{.NET (Core/Framework) · ReactJS · NextJS · React Native · SwiftUI · NodeJS · LangChain}
\cvitem{Databases}{MongoDB · DynamoDB · MySQL · PostgreSQL · MS SQL Server · ChromaDB}
\cvitem{Other}{Object oriented design · Data structures and algorithms · LLM + RAG integration · Computer Vision · Shell scripting · RESTful APIs · Git · GitHub CI/CD · AWS Serverless · Figma · WebGL · LangChain}
\section{Projects}
\cventry
{}
{Clarity Softphone}
{}
{\textit{Swift, SwiftUI, Linphone SDK, CallKit}}
{}
{A native iOS SIP softphone supporting UDP/TCP/TLS transports, CallKit-integrated call UX, and DTMF. Shipped to the App Store. · github.com/arshwaraich/softphone}
\vspace{1mm}
\cventry
{}
{Sun Timezone}
{}
{\textit{Swift, SwiftUI, Canvas, NextJS}}
{}
{An iOS app visualising multiple timezones along a sun-arc chart with a scrubbing time dial. Ported from an earlier NextJS web app (arshwaraich.github.io/time-zone) to native iOS using LLM coding agents; shipped to the App Store. · github.com/arshwaraich/Timezone}
\vspace{1mm}
\cventry
{}
{Flag Fusion}
{}
{\textit{NextJS, TypeScript, Amazon AWS, Stripe, Figma}}
{}
{A responsive web app to color any flag in the colors of another flag, built to test Meta's local LLM supported development. · github.com/arshwaraich/FlagFusion}
\vspace{1mm}
\section{Awards}
\cventry
{}
{One RBC Team Award}
{}
{\textit{2023 Q3, 2024 Q1, 2024 Q3}}
{}
{Recognized for work in the HSBC acquisition, FHSA delivery and the Direct Investing Home redesign project, improving cross-functional collaboration and achieving key milestones on time.\\Royal Bank of Canada}
\vspace{1mm}
\cventry
{}
{Certificate of Recognition}
{}
{\textit{April 2020}}
{}
{In recognition of contributions to innovative research and entrepreneurial activities at Seneca. Presented at the Annual Applied Research, Innovation \& Entrepreneurship Showcase.\\Seneca Applied Research}
\vspace{1mm}
\cventry
{}
{RBC AmpHacks Top 5}
{}
{\textit{October 2020}}
{}
{For creating a video-sharing app for seniors called SocialDisco.\\RBC AmpHacks}
\vspace{1mm}
\end{document}